Learning and comparing functional connectomes across subjects

### 2013-03-26 paper.tex
Use the latex preview package to avoid having latex hacks for figures

@@

%{{{------ Parcellation figure -----------------------------------------------
\begin{figure}
\includegraphics[width=.5\linewidth]{aal_atlas}%
\hfill%
\includegraphics[width=.5\linewidth]{ho_atlas}%

\includegraphics[width=.5\linewidth]{sulci_atlas}%
\hfill%
\includegraphics[width=.5\linewidth]{ncuts_atlas}%

\includegraphics[width=.5\linewidth]{smith_atlas}%
\hfill%
\includegraphics[width=.5\linewidth]{msdl_atlas}%

@@

%{{{------ Correlation matrices figure ---------------------------------------
\begin{figure}
\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
{\color{black!70}\fbox{#1}\color{black}}}%
\begin{minipage}{.666\linewidth}%
    \includegraphics[width=\linewidth]{group_emp_cov}%
    \raisebox{.606\linewidth}{%
	\hspace*{-.462\linewidth}%
	\photoframe{%
	%\setlength\fboxsep{1pt}%
	\colorbox{white}{%
	\raisebox{.003\linewidth}{%
	    \includegraphics[width=.455\linewidth]{group_emp_cov_3d_labels}}%
	\rule{0pt}{.387\linewidth}%
	}}%
    }
\end{minipage}%
\hspace*{1pt}%
\begin{minipage}{.33\linewidth}%
    \includegraphics[width=\linewidth]{group_emp_cov_no_confounds}%

    \includegraphics[width=\linewidth]{group_emp_cov_global_mean}%
\end{minipage}%

@@

%{{{------ Precision matrices figure -----------------------------------------
\begin{figure}
\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
{\color{black!70}\fbox{#1}\color{black}}}%
\begin{minipage}{.666\linewidth}%
    \includegraphics[width=\linewidth]{group_l21_prec}%
    \raisebox{.606\linewidth}{%
	\hspace*{-.462\linewidth}%
	\photoframe{%
	%\setlength\fboxsep{1pt}%
	\colorbox{white}{%
	\raisebox{.003\linewidth}{%
	    \includegraphics[width=.455\linewidth]{group_l21_prec_3d_labels}}%
	\rule{0pt}{.387\linewidth}%
	}}%
    }
\end{minipage}%
\hspace*{1pt}%
\begin{minipage}{.33\linewidth}%
    \includegraphics[width=\linewidth]{group_emp_prec}%

    \includegraphics[width=\linewidth]{group_l1_prec}%
\end{minipage}%

@@

%{{{------ Regressor in precision matrix -------------------------------------
\begin{figure}
\includegraphics[height=.499\linewidth]{group_l21_prec_no_confounds}%
\hfill%
\includegraphics[height=.499\linewidth]{group_l21_prec_global_mean}%

@@

%{{{------ Inter subject fluctuations ----------------------------------------
\begin{figure}
\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub00}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub29}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub01}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub07}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/cov_sub53}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_00}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
    }%
    \llap{
	\raisebox{.17\linewidth}{%
	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{a}. Correlation matrices}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub00}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub29}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub01}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub07}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub53}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_01}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
    }%
    \llap{
	\raisebox{.168\linewidth}{%
	    \bfseries\tiny 4\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{b}. Z score on difference}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub00}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub29}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub01}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub07}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/prec_sub53}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_00}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
    }%
    \llap{
	\raisebox{.17\linewidth}{%
	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{c}. Inverse-covariance matrices}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub00}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub29}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub01}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub07}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub53}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_01}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
    }%
    \llap{
	\raisebox{.168\linewidth}{%
	    \bfseries\tiny 4\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{d}. Z score on inverse-covariance}}%
	}%
    \hspace*{.993\linewidth}%
}

\hspace*{.5ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub00}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub29}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub01}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub07}%
\hspace*{-.2ex}%
\includegraphics[width=.196\linewidth]{inter_subj/res_sub53}%
\hspace*{.1ex}%
\raisebox{.005\linewidth}{%
    \includegraphics[width=.0186\linewidth]{cmap_01}%
    \llap{
	\raisebox{.003\linewidth}{%
	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
    }%
    \llap{
	\raisebox{.168\linewidth}{%
	    \bfseries\tiny 4\hspace*{.1ex}}%
    }%
}%
\llap{\rlap{
    \setlength\fboxsep{1pt}%
    \raisebox{.16\linewidth}{%
	\colorbox{black!10}{%
	    \sffamily\small\textbf{e}. Z score on residuals \scriptsize
		\raisebox{.2ex}{\cite{varoquaux2010b}}}}%
	}%
    \hspace*{.993\linewidth}%
}

@@

%{{{------ Integration measure -----------------------------------------------
\begin{figure}
\hspace*{2ex}%
\begin{minipage}{.19\linewidth}
    \center\sffamily
    {\small Integration:}

    0.554
\end{minipage}%
\begin{minipage}{.2\linewidth}
    \includegraphics[width=1.07\linewidth]{correlation_ex1}
\end{minipage}%
\hfill%
\begin{minipage}{.033\linewidth}
    \rule{0pt}{6.487\linewidth}%
    \includegraphics[width=\linewidth]{correlation_cmap}%
    \llap{\raisebox{.4ex}{\scriptsize\sffamily\bfseries 0}\hspace*{.54ex}}%
    \llap{\raisebox{10.1ex}{\scriptsize\sffamily\bfseries\color{white} 1}%
	    \hspace*{.54ex}}
\end{minipage}%
\hfill%
\begin{minipage}{.2\linewidth}
    \hspace*{-.07\linewidth}%
    \includegraphics[width=1.07\linewidth]{correlation_ex2}
\end{minipage}%
\begin{minipage}{.19\linewidth}
    \center\sffamily
    {\small Integration:}

    2.422
\end{minipage}%
\hspace*{2ex}%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For the final version: to output PDF figures from latex
%\usepackage[tightpage,active]{preview}

@@

%{{{------ Parcellation figure -----------------------------------------------
\begin{figure}
%PRE%\begin{preview}
%PRE%\includegraphics[width=.5\linewidth]{aal_atlas}%
%PRE%\hfill%
%PRE%\includegraphics[width=.5\linewidth]{ho_atlas}%
%PRE%
%PRE%\includegraphics[width=.5\linewidth]{sulci_atlas}%
%PRE%\hfill%
%PRE%\includegraphics[width=.5\linewidth]{ncuts_atlas}%
%PRE%
%PRE%\includegraphics[width=.5\linewidth]{smith_atlas}%
%PRE%\hfill%
%PRE%\includegraphics[width=.5\linewidth]{msdl_atlas}%
%PRE%\end{preview}
\includegraphics[width=\linewidth]{pg_0001}%

@@

%{{{------ Correlation matrices figure ---------------------------------------
\begin{figure}
%PRE%\begin{preview}
%PRE%\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
%PRE%{\color{black!70}\fbox{#1}\color{black}}}%
%PRE%\begin{minipage}{.666\linewidth}%
%PRE%    \includegraphics[width=\linewidth]{group_emp_cov}%
%PRE%    \raisebox{.606\linewidth}{%
%PRE%	\hspace*{-.462\linewidth}%
%PRE%	\photoframe{%
%PRE%	%\setlength\fboxsep{1pt}%
%PRE%	\colorbox{white}{%
%PRE%	\raisebox{.003\linewidth}{%
%PRE%	    \includegraphics[width=.455\linewidth]{group_emp_cov_3d_labels}}%
%PRE%	\rule{0pt}{.387\linewidth}%
%PRE%	}}%
%PRE%    }
%PRE%\end{minipage}%
%PRE%\hspace*{1pt}%
%PRE%\begin{minipage}{.33\linewidth}%
%PRE%    \includegraphics[width=\linewidth]{group_emp_cov_no_confounds}%
%PRE%
%PRE%    \includegraphics[width=\linewidth]{group_emp_cov_global_mean}%
%PRE%\end{minipage}%
%PRE%\end{preview}
\includegraphics[width=\linewidth]{pg_0002}%

@@

%{{{------ Precision matrices figure -----------------------------------------
\begin{figure}
%PRE%\begin{preview}
%PRE%\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
%PRE%{\color{black!70}\fbox{#1}\color{black}}}%
%PRE%\begin{minipage}{.666\linewidth}%
%PRE%    \includegraphics[width=\linewidth]{group_l21_prec}%
%PRE%    \raisebox{.606\linewidth}{%
%PRE%	\hspace*{-.462\linewidth}%
%PRE%	\photoframe{%
%PRE%	%\setlength\fboxsep{1pt}%
%PRE%	\colorbox{white}{%
%PRE%	\raisebox{.003\linewidth}{%
%PRE%	    \includegraphics[width=.455\linewidth]{group_l21_prec_3d_labels}}%
%PRE%	\rule{0pt}{.387\linewidth}%
%PRE%	}}%
%PRE%    }
%PRE%\end{minipage}%
%PRE%\hspace*{1pt}%
%PRE%\begin{minipage}{.33\linewidth}%
%PRE%    \includegraphics[width=\linewidth]{group_emp_prec}%
%PRE%
%PRE%    \includegraphics[width=\linewidth]{group_l1_prec}%
%PRE%\end{minipage}%
%PRE%\end{preview}
\includegraphics[width=\linewidth]{pg_0003}%

@@

%{{{------ Regressor in precision matrix -------------------------------------
\begin{figure}
%PRE%\begin{preview}
%PRE%\includegraphics[height=.499\linewidth]{group_l21_prec_no_confounds}%
%PRE%\hfill%
%PRE%\includegraphics[height=.499\linewidth]{group_l21_prec_global_mean}%
%PRE%\end{preview}
\includegraphics[width=\linewidth]{pg_0004}%

@@

%{{{------ Inter subject fluctuations ----------------------------------------
\begin{figure}
%PRE%\begin{preview}
%PRE%\hspace*{.5ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub00}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub29}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub01}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub07}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub53}%
%PRE%\hspace*{.1ex}%
%PRE%\raisebox{.005\linewidth}{%
%PRE%    \includegraphics[width=.0186\linewidth]{cmap_00}%
%PRE%    \llap{
%PRE%	\raisebox{.003\linewidth}{%
%PRE%	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
%PRE%    }%
%PRE%    \llap{
%PRE%	\raisebox{.17\linewidth}{%
%PRE%	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
%PRE%    }%
%PRE%}%
%PRE%\llap{\rlap{
%PRE%    \setlength\fboxsep{1pt}%
%PRE%    \raisebox{.16\linewidth}{%
%PRE%	\colorbox{black!10}{%
%PRE%	    \sffamily\small\textbf{a}. Correlation matrices}}%
%PRE%	}%
%PRE%    \hspace*{.993\linewidth}%
%PRE%}
%PRE%
%PRE%
%PRE%\hspace*{.5ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub00}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub29}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub01}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub07}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub53}%
%PRE%\hspace*{.1ex}%
%PRE%\raisebox{.005\linewidth}{%
%PRE%    \includegraphics[width=.0186\linewidth]{cmap_01}%
%PRE%    \llap{
%PRE%	\raisebox{.003\linewidth}{%
%PRE%	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
%PRE%    }%
%PRE%    \llap{
%PRE%	\raisebox{.168\linewidth}{%
%PRE%	    \bfseries\tiny 4\hspace*{.1ex}}%
%PRE%    }%
%PRE%}%
%PRE%\llap{\rlap{
%PRE%    \setlength\fboxsep{1pt}%
%PRE%    \raisebox{.16\linewidth}{%
%PRE%	\colorbox{black!10}{%
%PRE%	    \sffamily\small\textbf{b}. Z score on difference}}%
%PRE%	}%
%PRE%    \hspace*{.993\linewidth}%
%PRE%}
%PRE%
%PRE%\hspace*{.5ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub00}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub29}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub01}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub07}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub53}%
%PRE%\hspace*{.1ex}%
%PRE%\raisebox{.005\linewidth}{%
%PRE%    \includegraphics[width=.0186\linewidth]{cmap_00}%
%PRE%    \llap{
%PRE%	\raisebox{.003\linewidth}{%
%PRE%	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
%PRE%    }%
%PRE%    \llap{
%PRE%	\raisebox{.17\linewidth}{%
%PRE%	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
%PRE%    }%
%PRE%}%
%PRE%\llap{\rlap{
%PRE%    \setlength\fboxsep{1pt}%
%PRE%    \raisebox{.16\linewidth}{%
%PRE%	\colorbox{black!10}{%
%PRE%	    \sffamily\small\textbf{c}. Inverse-covariance matrices}}%
%PRE%	}%
%PRE%    \hspace*{.993\linewidth}%
%PRE%}
%PRE%
%PRE%\hspace*{.5ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub00}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub29}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub01}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub07}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub53}%
%PRE%\hspace*{.1ex}%
%PRE%\raisebox{.005\linewidth}{%
%PRE%    \includegraphics[width=.0186\linewidth]{cmap_01}%
%PRE%    \llap{
%PRE%	\raisebox{.003\linewidth}{%
%PRE%	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
%PRE%    }%
%PRE%    \llap{
%PRE%	\raisebox{.168\linewidth}{%
%PRE%	    \bfseries\tiny 4\hspace*{.1ex}}%
%PRE%    }%
%PRE%}%
%PRE%\llap{\rlap{
%PRE%    \setlength\fboxsep{1pt}%
%PRE%    \raisebox{.16\linewidth}{%
%PRE%	\colorbox{black!10}{%
%PRE%	    \sffamily\small\textbf{d}. Z score on inverse-covariance}}%
%PRE%	}%
%PRE%    \hspace*{.993\linewidth}%
%PRE%}
%PRE%
%PRE%
%PRE%
%PRE%\hspace*{.5ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub00}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub29}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub01}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub07}%
%PRE%\hspace*{-.2ex}%
%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub53}%
%PRE%\hspace*{.1ex}%
%PRE%\raisebox{.005\linewidth}{%
%PRE%    \includegraphics[width=.0186\linewidth]{cmap_01}%
%PRE%    \llap{
%PRE%	\raisebox{.003\linewidth}{%
%PRE%	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
%PRE%    }%
%PRE%    \llap{
%PRE%	\raisebox{.168\linewidth}{%
%PRE%	    \bfseries\tiny 4\hspace*{.1ex}}%
%PRE%    }%
%PRE%}%
%PRE%\llap{\rlap{
%PRE%    \setlength\fboxsep{1pt}%
%PRE%    \raisebox{.16\linewidth}{%
%PRE%	\colorbox{black!10}{%
%PRE%	    \sffamily\small\textbf{e}. Z score on residuals \scriptsize
%PRE%		\raisebox{.2ex}{\cite{varoquaux2010b}}}}%
%PRE%	}%
%PRE%    \hspace*{.993\linewidth}%
%PRE%}
%PRE%\end{preview}
\includegraphics[width=\linewidth]{pg_0005}%

@@

%{{{------ Integration measure -----------------------------------------------
\begin{figure}
%PRE%\begin{preview}
%PRE%\hspace*{2ex}%
%PRE%\begin{minipage}{.19\linewidth}
%PRE%    \center\sffamily
%PRE%    {\small Integration:}
%PRE%
%PRE%    0.554
%PRE%\end{minipage}%
%PRE%\begin{minipage}{.2\linewidth}
%PRE%    \includegraphics[width=1.07\linewidth]{correlation_ex1}
%PRE%\end{minipage}%
%PRE%\hfill%
%PRE%\begin{minipage}{.033\linewidth}
%PRE%    \rule{0pt}{6.487\linewidth}%
%PRE%    \includegraphics[width=\linewidth]{correlation_cmap}%
%PRE%    \llap{\raisebox{.4ex}{\scriptsize\sffamily\bfseries 0}\hspace*{.54ex}}%
%PRE%    \llap{\raisebox{10.1ex}{\scriptsize\sffamily\bfseries\color{white} 1}%
%PRE%	    \hspace*{.54ex}}
%PRE%\end{minipage}%
%PRE%\hfill%
%PRE%\begin{minipage}{.2\linewidth}
%PRE%    \hspace*{-.07\linewidth}%
%PRE%    \includegraphics[width=1.07\linewidth]{correlation_ex2}
%PRE%\end{minipage}%
%PRE%\begin{minipage}{.19\linewidth}
%PRE%    \center\sffamily
%PRE%    {\small Integration:}
%PRE%
%PRE%    2.422
%PRE%\end{minipage}%
%PRE%\hspace*{2ex}%
%PRE%\end{preview}
\includegraphics[width=\linewidth]{pg_0006}
